### 2016-09-23 stats.tex
Fix tests
We need to make sure that x, y, and z are never redefined with assumptions.

Using the facilities of the \texttt{sympy.stats} submodule, one can, for
example, calculate
%Using the above-mentioned features, it is easy to calculate, for example
the well known properties of maxwellian velocity distribution
\begin{verbatim}
>>> from sympy.stats import Maxwell, density
>>> kT, m, x = symbols("kT m x", positive=True)
>>> v = Maxwell("v", sqrt(kT/m))
>>> E(v)                                # mean velocity
2*sqrt(2)*sqrt(kT)/(sqrt(pi)*sqrt(m))
>>> E(v, evaluate=False)                # unevaluated mean velocity
Integral(sqrt(2)*m**(3/2)*v**3*exp(-m*v**2/(2*kT))/(sqrt(pi)*kT**(3/2)),
(v, 0, oo))
>>> E(m*v**2/2)                         # mean energy
3*kT/2
>>> solve(density(v)(x).diff(x), x)[0]  # most probable velocity
sqrt(2)*sqrt(kT)/sqrt(m)
\end{verbatim}

>>>>

Using the facilities of the \texttt{sympy.stats} submodule, one can, for
example, calculate
%Using the above-mentioned features, it is easy to calculate, for example
the well known properties of maxwellian velocity distribution
\begin{verbatim}
>>> from sympy.stats import Maxwell, density
>>> kT, m, t = symbols("kT m t", positive=True)
>>> v = Maxwell("v", sqrt(kT/m))
>>> E(v)                                # mean velocity
2*sqrt(2)*sqrt(kT)/(sqrt(pi)*sqrt(m))
>>> E(v, evaluate=False)                # unevaluated mean velocity
Integral(sqrt(2)*m**(3/2)*v**3*exp(-m*v**2/(2*kT))/(sqrt(pi)*kT**(3/2)),
(v, 0, oo))
>>> E(m*v**2/2)                         # mean energy
3*kT/2
>>> solve(density(v)(t).diff(t), t)[0]  # most probable velocity
sqrt(2)*sqrt(kT)/sqrt(m)
\end{verbatim}
